A weakly structured stem for human origins in Africa

### 2022-03-10 paper.tex
Update paper.tex
bold labels in figure 1

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig1.pdf}
    \caption[width=\textwidth]{
        \textbf{Genetic diversity across Africa.}
        (A) Select populations from the 1000 Genomes and African Diversity Reference Panels
        illustrate diversity from western, eastern and southern Africa.
        We chose representatives from each region to build parameterized models,
        including the newly-sequenced Nama from South Africa, Mende
        from Sierre Leone, Gumuz, Oromo and Amhara from Ethiopia, and the
        British and Vindija Neanderthal individual.
        (B, C) PCA highlights the range of genetic divergence anchored 
        by western Africans, Nama, Gumuz and the British.
        Percentages show variance explained by each principal component.
        (D) \texttt{ADMIXTURE} illustrates signatures of recent gene flow in Africa
        which reflect colonial-period migration into the Nama,
        Back-to-Africa gene flow among some Ethiopians, and Khoe-San admixture in the Zulu.
        \comment{How did you land on the best fit k? Show scree plot of CV errors, or otherwise justify choice}
    }
    \label{fig:1}
\end{figure}

@@

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb}
(see also Section \ref{sec:orpho_diff}).
This correspondence allows predictions of our model to be related to the fossil record.
The fossil record of Africa is sparse during the time period of the stems, but of the
available fossils, some are very similar to contemporary humans
(e.g., from Omo Kibish, Ethiopia \citep{Day1969-rh,Vidal2022-qe}),
others are similar in some features but not others
(e.g., from Jebel Irhoud, Morocco \citep{Hublin2017-cq,Richter2017-zu}),
and others are very different
(e.g., from Dinaledi, South Africa \citep{Berger2015-bq,Dirks2017-uk}) in morphology.
If, as our model predicts, the
genetic differences between the stems were comparable to those among
contemporary human populations, the most morphologically divergent fossils are unlikely to
represent branches that contributed appreciably to contemporary human
ancestries.

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig1.pdf}
    \caption[width=\textwidth]{
        \textbf{Genetic diversity across Africa.}
        (A) Select populations from the 1000 Genomes and African Diversity Reference Panels
        illustrate diversity from western, eastern and southern Africa.
        We chose representatives from each region (bold labels)
        to build parameterized models,
        including the newly-sequenced Nama from South Africa, Mende
        from Sierre Leone, Gumuz, Oromo and Amhara from Ethiopia, and the
        British and Vindija Neanderthal individual.
        (B, C) PCA highlights the range of genetic divergence anchored 
        by western Africans, Nama, Gumuz and the British.
        Percentages show variance explained by each principal component.
        (D) \texttt{ADMIXTURE} illustrates signatures of recent gene flow in Africa
        which reflect colonial-period migration into the Nama,
        Back-to-Africa gene flow among some Ethiopians, and Khoe-San admixture in the Zulu.
        \comment{How did you land on the best fit k? Show scree plot of CV errors, or otherwise justify choice}
    }
    \label{fig:1}
\end{figure}

@@

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb}
(see also Section \ref{sec:morpho_diff}).
This correspondence allows predictions of our model to be related to the fossil record.
The fossil record of Africa is sparse during the time period of the stems, but of the
available fossils, some are very similar to contemporary humans
(e.g., from Omo Kibish, Ethiopia \citep{Day1969-rh,Vidal2022-qe}),
others are similar in some features but not others
(e.g., from Jebel Irhoud, Morocco \citep{Hublin2017-cq,Richter2017-zu}),
and others are very different
(e.g., from Dinaledi, South Africa \citep{Berger2015-bq,Dirks2017-uk}) in morphology.
If, as our model predicts, the
genetic differences between the stems were comparable to those among
contemporary human populations, the most morphologically divergent fossils are unlikely to
represent branches that contributed appreciably to contemporary human
ancestries.
